Stepwise Multiple Regressions

### 2021-02-10 Stepwise Multiple Regressions.Rmd
interaction term!

#Select the columns that we want to feed into the model for simplicity
m1_crust_simple <- aoc_setup %>%
  filter(!effect_f == "NA") %>%
  filter(!acute.chronic_f == "Unavailable") %>%
  filter(bio.org == "organism") %>%
  filter(!environment == "Terrestrial") %>%
  filter(lvl1_f == "Fitness") %>%
  filter(!size_f == "Not Reported") %>%
  mutate(logdose.mg.L.master = log10(dose.mg.L.master))

#Fit the full model
m1_crust_model_dose <- glm(effect_10 ~ logdose.mg.L.master + size.length.um.used.for.conversions, data = m1_crust_simple, na.action = "na.exclude", family = "binomial")

@@

#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)

range(m1_crust_simple$logdose.mg.L.master, na.rm = TRUE)
#[1] -11.638272   8.171552
# generate sequence of values between range in increments of 100 to give smooth appearance to model
xdose <- seq(-11.638272 ,8.171552, 0.1)
ydose <- predict(m1_crust_model_dose, 
                 list(logdose.mg.L.master = xdose), 
                 type = "response")
#ggplot with logistic data
 plot(m1_crust_simple$logdose.mg.L.master, m1_crust_simple$effect_10, pch = 16, xlab = "log dose (mg/L)", ylab = "effect")
# lines(xdose, ydose)

ggplot(m1_crust_simple, aes(x = logdose.mg.L.master, y = effect_10))+
  geom_point() +
  stat_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE)

>>>>

#Select the columns that we want to feed into the model for simplicity
m1_crust <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.mg.L.master = log10(dose.mg.L.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.mg.L.master, size.length.um.used.for.conversions)) %>% 
  drop_na()

#Fit the full model
m1_crust_model_dose <- glm(effect_10 ~ logdose.mg.L.master * size.length.um.used.for.conversions, data = m1_crust, na.action = "na.exclude", family = "binomial")

@@

```{r}
#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=TRUE)
```

```{r}
#alternative method using ggplot

#get probabilities
m1 <- m1_crust %>% 
  mutate(prob = predict(m1_crust_model_dose,
                        type = "response"))

# plot
ggplot(m1, aes(x = logdose.mg.L.master, y = effect_10, color = size.length.um.used.for.conversions))+
  geom_jitter() +
  geom_smooth(method = 'glm',
              aes(x = logdose.mg.L.master, y = prob), #use predicted NOEC probability
              method.args = list(family = binomial(link = 'logit')),
              se = FALSE, color = 'red') #+
  # geom_smooth(method = 'glm',
  #             method.args = list(family = binomial(link = 'probit')),
  #             se = FALSE, color = 'green') +
  # stat_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE)
```
